\begin{enumerate}
	% question 1
	\item What advantages do NAT Gateways have over NAT Instances? (Select TWO.)
	\begin{itemize}
		\item Managed for you by AWS
		\item Highly available within each AZ
		\item Can be scaled up manually
		\item Can be used as a bastion host
		\item Can be assigned to security groups
	\end{itemize}

	% question 2
	\item A Cloud Practitioner wants to configure the AWS CLI for programmatic access to AWS services. Which credential components are required? (Select TWO.)
	\begin{itemize}
		\item A private key
		\item A secret access key
		\item An access key ID
		\item A public key
		\item An IAM Role
	\end{itemize}

	% question 3
	\item How can a Solutions Architect reduce the latency between end-users and applications or content? (Select TWO.)
	\begin{itemize}
		\item Deploy applications in multiple AZs
		\item Deploy applications in regions closest to the end-users
		\item Use larger EC2 instance types for the applications
		\item Use Amazon CloudFront to cache content closer to end-users
		\item Use S3 Transfer Acceleration to improve application performance
	\end{itemize}

	% question 4
	\item Which of the statements below is correct in relation to Consolidated Billing? (choose 3)
	\begin{itemize}
		\item You pay a fee per linked account
		\item You can combine usage and share volume pricing discounts
		\item You are not charged a fee
		\item You receive a single bill for multiple accounts
		\item You receive one bill per AWS account
	\end{itemize}

	% question 5
	\item Which service supports the resolution of public domain names to IP addresses or AWS resources?
	\begin{itemize}
		\item Amazon Route 53
		\item Amazon SNS
		\item Amazon CloudFront
		\item Hosted Zones
	\end{itemize}

	% question 6
	\item Which Amazon S3 storage classes should be used for storing data for long time periods when immediate access is not required at the LOWEST cost? (Select TWO.)
	\begin{itemize}
		\item Amazon S3 One Zone-Infrequent Access (S3 One Zone-IA)
		\item Amazon S3 Standard
		\item Amazon S3 Glacier Deep Archive
		\item Amazon S3 Standard-Infrequent Access (S3 Standard-IA)
		\item Amazon S3 Glacier
	\end{itemize}

	% question 7
	\item When storing sensitive company data in Amazon S3, which security best practices should customers follow?
	\begin{itemize}
		\item Enable requester pays to reduce costs.
		\item Enable S3 server-side encryption on the S3 bucket.
		\item Enable AWS WAF to restrict access to the bucket.
		\item Enable cross-Region replication on the S3 bucket.
	\end{itemize}

	% question 8
	\item What speeds is AWS Direct Connect offered at by AWS? (Select TWO.)
	\begin{itemize}
		\item 100 Mbps
		\item 50 Mbps
		\item 1 Gbps
		\item 10 Gbps
		\item 100 Gbps
	\end{itemize}

	% question 9
	\item Which types of root storage devices are available for Amazon EC2 instances? (Select TWO.)
	\begin{itemize}
		\item EFS file system
		\item RAM
		\item EBS volume
		\item S3 Bucket
		\item Instance Store
	\end{itemize}

	% question 10
	\item Which team is available to support AWS customers on an Enterprise support plan with account issues?
	\begin{itemize}
		\item AWS Technical Account Manager
		\item AWS Billing and Accounts
		\item AWS Concierge
		\item AWS Technical Support
	\end{itemize}

	% question 11
	\item What are the benefits of using the AWS Managed Services? (Select TWO.)
	\begin{itemize}
		\item Designed for small businesses
		\item Baseline integration with ITSM tools
		\item Support for all AWS services
		\item Alignment with ITIL processes
		\item Managed applications so you can focus on infrastructure
	\end{itemize}

	% question 12
	\item Which file format is used to write AWS Identity and Access Management (IAM) policies?
	\begin{itemize}
		\item XML
		\item DOC
		\item JBOD
		\item JSON
	\end{itemize}

	% question 13
	\item To optimize pricing or ensure capacity is available reservations can be applied to which of the following services? (Select TWO.)
	\begin{itemize}
		\item Amazon EC2
		\item AWS Lambda
		\item Amazon EBS
		\item Amazon S3
		\item Amazon RDS
	\end{itemize}

	% question 14
	\item Which AWS service uses a highly secure hardware storage device to store encryption keys?
	\begin{itemize}
		\item AWS WAF
		\item AWS IAM
		\item AWS CloudHSM
		\item Amazon Cloud Directory
	\end{itemize}

	% question 15
	\item You have been running an on-demand Amazon EC2 instance running Linux for 4hrs, 5 minutes and 6 seconds. How much time will you be billed for?
	\begin{itemize}
		\item 4hrs, 5mins, and 6 seconds
		\item 5hrs
		\item 4hrs, 6mins
		\item 4hrs
	\end{itemize}

	% question 16
	\item A Cloud Practitioner requires a simple method to identify if unrestricted access to resources has been allowed by security groups. Which service can the Cloud Practitioner use?
	\begin{itemize}
		\item AWS CloudTrail
		\item VPC Flow Logs
		\item AWS Trusted Advisor
		\item Amazon CloudWatch
	\end{itemize}

	% question 17
	\item How should an organization deploy an application running on multiple EC2 instances to ensure that a power failure does not cause an application outage?
	\begin{itemize}
		\item Launch the EC2 instances into Edge Locations
		\item Launch the EC2 instances into different Availability Zones
		\item Launch the EC2 instances into different VPCs
		\item Launch the EC2 instances in separate regions
	\end{itemize}

	% question 18
	\item A company recently setup an organization in AWS Organizations with one member account. Who pays for usage incurred by users in the AWS accounts?
	\begin{itemize}
		\item The owner of the member account pays for usage within their account.
		\item The owner of the master account pays for all usage across accounts.
		\item The owner of the master account pays for usage in the master account only.
		\item The owner of the member account pays for all usage across accounts.
	\end{itemize}

	% question 19
	\item What type of storage is provided by Amazon EBS?
	\begin{itemize}
		\item Block
		\item File
		\item Relational
		\item Object
	\end{itemize}

	% question 20
	\item Which of the following is a method of backup available in the AWS cloud?
	\begin{itemize}
		\item EBS Snapshots
		\item Availability Zones
		\item EFS File Systems
		\item Route 53 Alias Record
	\end{itemize}

	% question 21
	\item What are two components of Amazon S3? (Select TWO.)
	\begin{itemize}
		\item Objects
		\item Block devices
		\item Directories
		\item Buckets
		\item File systems
	\end{itemize}

	% question 22
	\item Which database service is a NoSQL type of database that is fully managed?
	\begin{itemize}
		\item Amazon DynamoDB
		\item Amazon RDS
		\item Amazon ElastiCache
		\item Amazon RedShift
	\end{itemize}

	% question 23
	\item An AWS customer wishes to purchase unused Amazon EC2 capacity at a discounted rate. Which pricing plan should they choose?
	\begin{itemize}
		\item Reserved Instances
		\item On-Demand Instances
		\item Dedicated Instances
		\item Spot Instances
	\end{itemize}

	% question 24
	\item A developer needs a way to automatically provision a collection of AWS resources. Which AWS service is primarily used for deploying infrastructure as code?
	\begin{itemize}
		\item AWS CodeDeploy
		\item Amazon CloudFormation
		\item Jenkins
		\item AWS Elastic Beanstalk
	\end{itemize}

	% question 25
	\item What is the most cost-effective Amazon S3 storage tier for data that is not often accessed but requires high availability?
	\begin{itemize}
		\item Amazon S3 Standard
		\item Amazon S3 Standard-IA
		\item Amazon S3 One Zone-IA
		\item Amazon Glacier
	\end{itemize}

	% question 26
	\item What is required to enable an EC2 instance in a public subnet to access the Internet? (Select TWO.)
	\begin{itemize}
		\item A public IP address
		\item A VPN connection
		\item A route to an Internet Gateway
		\item A NAT Gateway
		\item A NAT Instance
	\end{itemize}

	% question 27
	\item You need to provision a single EBS volume that is 500 GiB in size and needs to support 20,000 IOPS. Which EBS volume type will you select?
	\begin{itemize}
		\item Throughput Optimized HDD
		\item Provisioned IOPS SSD
		\item Cold HDD
		\item General Purpose SSD
	\end{itemize}

	% question 28
	\item Which EC2 tenancy model gives you visibility and control over how instances are placed on a server?
	\begin{itemize}
		\item Dedicated EC2
		\item Dedicated Hosts
		\item Dedicated Instances
		\item Dedicated Tenancy
	\end{itemize}

	% question 29
	\item What billing timeframes are available for Amazon EC2 on-demand instances? (Select TWO.)
	\begin{itemize}
		\item Per day
		\item Per week
		\item Per second
		\item Per minute
		\item Per hour
	\end{itemize}

	% question 30
	\item Which AWS service is part of the suite of "serverless" services and runs code as functions?
	\begin{itemize}
		\item Amazon ECS
		\item Amazon EKS
		\item AWS Lambda
		\item AWS CodeCommit
	\end{itemize}

	% question 31
	\item Which type of security control can be used to deny network access from a specific IP address?
	\begin{itemize}
		\item AWS Shield
		\item AWS WAF
		\item Network ACL
		\item Security Group
	\end{itemize}

	% question 32
	\item Which AWS database service provides a fully managed data warehouse that can be analyzed using SQL tools and business intelligence tools?
	\begin{itemize}
		\item Amazon ElastiCache
		\item Amazon RDS
		\item Amazon DynamoDB
		\item Amazon RedShift
	\end{itemize}

	% question 33
	\item Which of the following compliance programs allows the AWS environment to process, maintain, and store protected health information?
	\begin{itemize}
		\item PCI DSS
		\item SOC 1
		\item ISO 27001
		\item HIPAA
	\end{itemize}

	% question 34
	\item Which AWS support plans provide 24x7 access to customer service?
	\begin{itemize}
		\item Developer
		\item Business
		\item Basic
		\item All plans
	\end{itemize}

	% question 35
	\item Your CTO wants to move to cloud. What cost advantages are there to moving to cloud?
	\begin{itemize}
		\item You can reduce your marketing costs
		\item You don’t need to pay for application licensing
		\item You get free data transfer into and out of the cloud
		\item You provision only what you need and adjust to peak load
	\end{itemize}

	% question 36
	\item What do you need to log into the AWS console?
	\begin{itemize}
		\item Certificate
		\item Access key and secret ID
		\item Key pair
		\item User name and password
	\end{itemize}

	% question 37
	\item How can a company facilitate the sharing of data over private connections between two accounts they own within a region?
	\begin{itemize}
		\item Configure matching CIDR address ranges
		\item Create a VPC peering connection
		\item Create a subnet peering connection
		\item Create an internal ELB
	\end{itemize}

	% question 38
	\item What is the scope of an Amazon Virtual Private Cloud (VPC)?
	\begin{itemize}
		\item It spans multiple subnets
		\item It spans a single CIDR block
		\item It spans all Availability Zones in all regions
		\item It spans all Availability Zones within a region
	\end{itemize}

	% question 39
	\item Which AWS service can be used to ensure the persistence of in-flight transactions independently of any single application component?
	\begin{itemize}
		\item Amazon SQS
		\item AWS ElastiCache
		\item Amazon DynamoDB
		\item AWS CloudFormation
	\end{itemize}

	% question 40
	\item What are the fundamental charges for Elastic Block Store (EBS) volumes? (Select TWO.)
	\begin{itemize}
		\item The amount of data storage consumed
		\item The amount of data storage provisioned
		\item Number of snapshots
		\item Inbound data transfer
		\item Provisioned IOPS
	\end{itemize}

	% question 41
	\item Your company has recently migrated to AWS. How can your CTO monitor the organization’s costs?
	\begin{itemize}
		\item AWS Simple Monthly calculator
		\item AWS Cost Explorer
		\item AWS CloudTrail
		\item AWS Consolidated Billing
	\end{itemize}

	% question 42
	\item Your organization has offices around the world and some employees travel between offices. How should their accounts be setup?
	\begin{itemize}
		\item Set the user account as a “global” account when created
		\item Create a separate account in IAM within each region in which they will travel
		\item Enable MFA for the accounts
		\item IAM is a global service, just create the users in one place
	\end{itemize}

	% question 43
	\item To which destinations can Amazon S3 NOT send event notifications? (Select TWO.)
	\begin{itemize}
		\item Lambda functions
		\item CloudWatch
		\item SQS Queue
		\item SNS Topics
		\item DynamoDB Table
	\end{itemize}

	% question 44
	\item What types of origins are supported by Amazon CloudFront? (Select TWO.)
	\begin{itemize}
		\item Elastic Load Balancer
		\item EBS volume
		\item EC2 instance
		\item Elastic File System
		\item S3 object
	\end{itemize}

	% question 45
	\item Which AWS technology can be referred to as a “virtual hard disk in the cloud”?
	\begin{itemize}
		\item Amazon EFS Filesystem
		\item Amazon S3 Bucket
		\item Amazon EBS volume
		\item Amazon ENI
	\end{itemize}

	% question 46
	\item Where are Amazon EBS snapshots stored?
	\begin{itemize}
		\item On Amazon S3
		\item Within the EBS block store
		\item On an Amazon EFS filesystem
		\item On an Amazon EBS instance store
	\end{itemize}

	% question 47
	\item What tool provides real time guidance to help you provision your resources following best practices in the areas of cost optimization, performance, security and fault tolerance?
	\begin{itemize}
		\item Amazon IAM
		\item AWS Trusted Advisor
		\item AWS Personal Health Dashboard
		\item AWS Inspector
	\end{itemize}

	% question 48
	\item What is the best way for an organization to automate the creation, retention, and deletion of EBS snapshots?
	\begin{itemize}
		\item Create a CloudFormation template
		\item Use Amazon DLM
		\item Use S3 lifecycle policies
		\item Create a script
	\end{itemize}

	% question 49
	\item Which AWS service is designed to be used for operational analytics?
	\begin{itemize}
		\item Amazon EMR
		\item Amazon Athena
		\item Amazon Elasticsearch Service
		\item Amazon QuickSight
	\end{itemize}

	% question 50
	\item Which AWS services can be utilized at no cost? (Select TWO.)
	\begin{itemize}
		\item Amazon CloudFront
		\item Amazon RedShift
		\item Identity and Access Management (IAM)
		\item Amazon VPC
		\item Amazon S3
	\end{itemize}

	% question 51
	\item An Amazon EC2 instance running the Amazon Linux 2 AMI is billed in what increment?
	\begin{itemize}
		\item Per CPU
		\item Per hour
		\item Per second
		\item Per GB
	\end{itemize}

	% question 52
	\item Which type of storage stores objects comprised of key, value pairs?
	\begin{itemize}
		\item Amazon EFS
		\item Amazon EBS
		\item Amazon DynamoDB
		\item Amazon S3
	\end{itemize}

	% question 53
	\item Which Amazon EC2 Reserved Instance type enables you to match your capacity reservation to predictable recurring dates and times?
	\begin{itemize}
		\item Standard RI
		\item Customized RI
		\item Convertible RI
		\item Scheduled RI
	\end{itemize}

	% question 54
	\item Which statement is correct in relation to the AWS Shared Responsibility Model?
	\begin{itemize}
		\item AWS are responsible for encrypting customer data
		\item Customers are responsible for security of the cloud
		\item AWS are responsible for the security of regions and availability zones
		\item Customers are responsible for patching storage systems
	\end{itemize}

	% question 55
	\item Which type of data storage system is typically considered to hold "structured" data?
	\begin{itemize}
		\item Relational database
		\item Email system
		\item File system
		\item Non-relational database
	\end{itemize}

	% question 56
	\item What is an example of scaling vertically?
	\begin{itemize}
		\item AWS Auto Scaling adding more EC2 instances
		\item AWS Lambda adding concurrently executing functions
		\item Increasing the instance size with Amazon RDS
		\item Adding read replicas to an Amazon RDS database
	\end{itemize}

	% question 57
	\item Which Amazon namespace is used to uniquely identify AWS resources?
	\begin{itemize}
		\item ACL
		\item ARN
		\item API
		\item AMI
	\end{itemize}

	% question 58
	\item Which of the below is Amazon's proprietary RDS database?
	\begin{itemize}
		\item Aurora
		\item DynamoDB
		\item MySQL
		\item MariaDB
	\end{itemize}

	% question 59
	\item 
	\begin{itemize}
		\item Amazon CloudFront
		\item Amazon Route 53
		\item Amazon S3
		\item AWS IAM
		\item Amazon EC2
	\end{itemize}

	% question 60
	\item Which resource should you use to access AWS security and compliance reports?
	\begin{itemize}
		\item AWS IAM
		\item AWS Organizations
		\item AWS Business Associate Addendum (BAA)
		\item AWS Artifact
	\end{itemize}

	% question 61
	\item Which services are integrated with KMS encryption? (Select TWO.)
	\begin{itemize}
		\item Amazon RDS
		\item Amazon EC2
		\item Amazon EBS
		\item Amazon SWF
		\item AWS CloudFormation
	\end{itemize}

	% question 62
	\item Which of the options below are recommendations in the reliability pillar of the well-architected framework? (Select TWO.)
	\begin{itemize}
		\item Automatically recover from failure
		\item Use ad-hoc recovery procedures
		\item Attempt to accurately estimate capacity requirements
		\item Scale vertically to increase aggregate system availability
		\item Manage change in automation
	\end{itemize}

	% question 63
	\item Which service can be used to manage configuration versions?
	\begin{itemize}
		\item AWS Service Catalog
		\item AWS Config
		\item AWS Artifact
		\item Amazon Inspector
	\end{itemize}

	% question 64
	\item Which service can be used to improve performance for users around the world?
	\begin{itemize}
		\item AWS LightSail
		\item Amazon Connect
		\item Amazon CloudFront
		\item Amazon ElastiCache
	\end{itemize}

	% question 65
	\item Which of the following is an advantage of cloud computing compared to deploying your own infrastructure on-premise?
	\begin{itemize}
		\item Flexibility to choose your own hardware
		\item Paying only for what you use
		\item Ability to choose bespoke infrastructure configurations
		\item Spend using a CAPEX model
	\end{itemize}

\end{enumerate}