\begin{enumerate}
	% question 1
	\item What advantages do NAT Gateways have over NAT Instances? (Select TWO.)

	\begin{itemize}
	\item Managed for you by AWS
	\item Highly available within each AZ
\end{itemize}

	% question 2
	\item A Cloud Practitioner wants to configure the AWS CLI for programmatic access to AWS services. Which credential components are required? (Select TWO.)

	\begin{itemize}
	\item A secret access key
	\item An access key ID
\end{itemize}

	% question 3
	\item How can a Solutions Architect reduce the latency between end-users and applications or content? (Select TWO.)

	\begin{itemize}
	\item Deploy applications in regions closest to the end-users
	\item Use Amazon CloudFront to cache content closer to end-users
\end{itemize}

	% question 4
	\item Which of the statements below is correct in relation to Consolidated Billing? (choose 3)

	\begin{itemize}
	\item You can combine usage and share volume pricing discounts
	\item You are not charged a fee
	\item You receive a single bill for multiple accounts
\end{itemize}

	% question 5
	\item Which service supports the resolution of public domain names to IP addresses or AWS resources?

	\begin{itemize}
	\item Amazon Route 53
\end{itemize}

	% question 6
	\item Which Amazon S3 storage classes should be used for storing data for long time periods when immediate access is not required at the LOWEST cost? (Select TWO.)

	\begin{itemize}
	\item Amazon S3 Glacier Deep Archive
	\item Amazon S3 Glacier
\end{itemize}

	% question 7
	\item When storing sensitive company data in Amazon S3, which security best practices should customers follow?

	\begin{itemize}
	\item Enable S3 server-side encryption on the S3 bucket.
\end{itemize}

	% question 8
	\item What speeds is AWS Direct Connect offered at by AWS? (Select TWO.)

	\begin{itemize}
	\item 1 Gbps
	\item 10 Gbps
\end{itemize}

	% question 9
	\item Which types of root storage devices are available for Amazon EC2 instances? (Select TWO.)

	\begin{itemize}
	\item EBS volume
	\item Instance Store
\end{itemize}

	% question 10
	\item Which team is available to support AWS customers on an Enterprise support plan with account issues?

	\begin{itemize}
	\item AWS Concierge
\end{itemize}

	% question 11
	\item What are the benefits of using the AWS Managed Services? (Select TWO.)

	\begin{itemize}
	\item Baseline integration with ITSM tools
	\item Alignment with ITIL processes
\end{itemize}

	% question 12
	\item Which file format is used to write AWS Identity and Access Management (IAM) policies?

	\begin{itemize}
	\item JSON
\end{itemize}

	% question 13
	\item To optimize pricing or ensure capacity is available reservations can be applied to which of the following services? (Select TWO.)

	\begin{itemize}
	\item Amazon EC2
	\item Amazon RDS
\end{itemize}

	% question 14
	\item Which AWS service uses a highly secure hardware storage device to store encryption keys?

	\begin{itemize}
	\item AWS CloudHSM
\end{itemize}

	% question 15
	\item You have been running an on-demand Amazon EC2 instance running Linux for 4hrs, 5 minutes and 6 seconds. How much time will you be billed for?

	\begin{itemize}
	\item 4hrs, 5mins, and 6 seconds
\end{itemize}

	% question 16
	\item A Cloud Practitioner requires a simple method to identify if unrestricted access to resources has been allowed by security groups. Which service can the Cloud Practitioner use?

	\begin{itemize}
	\item AWS Trusted Advisor
\end{itemize}

	% question 17
	\item How should an organization deploy an application running on multiple EC2 instances to ensure that a power failure does not cause an application outage?

	\begin{itemize}
	\item Launch the EC2 instances into different Availability Zones
\end{itemize}

	% question 18
	\item A company recently setup an organization in AWS Organizations with one member account. Who pays for usage incurred by users in the AWS accounts?

	\begin{itemize}
	\item The owner of the master account pays for all usage across accounts.
\end{itemize}

	% question 19
	\item What type of storage is provided by Amazon EBS?

	\begin{itemize}
	\item Block
\end{itemize}

	% question 20
	\item Which of the following is a method of backup available in the AWS cloud?

	\begin{itemize}
	\item EBS Snapshots
\end{itemize}

	% question 21
	\item What are two components of Amazon S3? (Select TWO.)

	\begin{itemize}
	\item Objects
	\item Buckets
\end{itemize}

	% question 22
	\item Which database service is a NoSQL type of database that is fully managed?

	\begin{itemize}
	\item Amazon DynamoDB
\end{itemize}

	% question 23
	\item An AWS customer wishes to purchase unused Amazon EC2 capacity at a discounted rate. Which pricing plan should they choose?

	\begin{itemize}
	\item Spot Instances
\end{itemize}

	% question 24
	\item A developer needs a way to automatically provision a collection of AWS resources. Which AWS service is primarily used for deploying infrastructure as code?

	\begin{itemize}
	\item Amazon CloudFormation
\end{itemize}

	% question 25
	\item What is the most cost-effective Amazon S3 storage tier for data that is not often accessed but requires high availability?

	\begin{itemize}
	\item Amazon S3 Standard-IA
\end{itemize}

	% question 26
	\item What is required to enable an EC2 instance in a public subnet to access the Internet? (Select TWO.)

	\begin{itemize}
	\item A public IP address
	\item A route to an Internet Gateway
\end{itemize}

	% question 27
	\item You need to provision a single EBS volume that is 500 GiB in size and needs to support 20,000 IOPS. Which EBS volume type will you select?

	\begin{itemize}
	\item Provisioned IOPS SSD
\end{itemize}

	% question 28
	\item Which EC2 tenancy model gives you visibility and control over how instances are placed on a server?

	\begin{itemize}
	\item Dedicated Hosts
\end{itemize}

	% question 29
	\item What billing timeframes are available for Amazon EC2 on-demand instances? (Select TWO.)

	\begin{itemize}
	\item Per second
	\item Per hour
\end{itemize}

	% question 30
	\item Which AWS service is part of the suite of "serverless" services and runs code as functions?

	\begin{itemize}
	\item AWS Lambda
\end{itemize}

	% question 31
	\item Which type of security control can be used to deny network access from a specific IP address?

	\begin{itemize}
	\item Network ACL
\end{itemize}

	% question 32
	\item Which AWS database service provides a fully managed data warehouse that can be analyzed using SQL tools and business intelligence tools?

	\begin{itemize}
	\item Amazon RedShift
\end{itemize}

	% question 33
	\item Which of the following compliance programs allows the AWS environment to process, maintain, and store protected health information?

	\begin{itemize}
	\item HIPAA
\end{itemize}

	% question 34
	\item Which AWS support plans provide 24x7 access to customer service?

	\begin{itemize}
	\item All plans
\end{itemize}

	% question 35
	\item Your CTO wants to move to cloud. What cost advantages are there to moving to cloud?

	\begin{itemize}
	\item You provision only what you need and adjust to peak load
\end{itemize}

	% question 36
	\item What do you need to log into the AWS console?

	\begin{itemize}
	\item User name and password
\end{itemize}

	% question 37
	\item How can a company facilitate the sharing of data over private connections between two accounts they own within a region?

	\begin{itemize}
	\item Create a VPC peering connection
\end{itemize}

	% question 38
	\item What is the scope of an Amazon Virtual Private Cloud (VPC)?

	\begin{itemize}
	\item It spans all Availability Zones within a region
\end{itemize}

	% question 39
	\item Which AWS service can be used to ensure the persistence of in-flight transactions independently of any single application component?

	\begin{itemize}
	\item Amazon SQS
\end{itemize}

	% question 40
	\item What are the fundamental charges for Elastic Block Store (EBS) volumes? (Select TWO.)

	\begin{itemize}
	\item The amount of data storage provisioned
	\item Provisioned IOPS
\end{itemize}

	% question 41
	\item Your company has recently migrated to AWS. How can your CTO monitor the organization’s costs?

	\begin{itemize}
	\item AWS Cost Explorer
\end{itemize}

	% question 42
	\item Your organization has offices around the world and some employees travel between offices. How should their accounts be setup?

	\begin{itemize}
	\item IAM is a global service, just create the users in one place
\end{itemize}

	% question 43
	\item To which destinations can Amazon S3 NOT send event notifications? (Select TWO.)

	\begin{itemize}
	\item CloudWatch
	\item DynamoDB Table
\end{itemize}

	% question 44
	\item What types of origins are supported by Amazon CloudFront? (Select TWO.)

	\begin{itemize}
	\item Elastic Load Balancer
	\item EC2 instance
\end{itemize}

	% question 45
	\item Which AWS technology can be referred to as a “virtual hard disk in the cloud”?

	\begin{itemize}
	\item Amazon EBS volume
\end{itemize}

	% question 46
	\item Where are Amazon EBS snapshots stored?

	\begin{itemize}
	\item On Amazon S3
\end{itemize}

	% question 47
	\item What tool provides real time guidance to help you provision your resources following best practices in the areas of cost optimization, performance, security and fault tolerance?

	\begin{itemize}
	\item AWS Trusted Advisor
\end{itemize}

	% question 48
	\item What is the best way for an organization to automate the creation, retention, and deletion of EBS snapshots?

	\begin{itemize}
	\item Use Amazon DLM
\end{itemize}

	% question 49
	\item Which AWS service is designed to be used for operational analytics?

	\begin{itemize}
	\item Amazon Elasticsearch Service
\end{itemize}

	% question 50
	\item Which AWS services can be utilized at no cost? (Select TWO.)

	\begin{itemize}
	\item Identity and Access Management (IAM)
	\item Amazon VPC
\end{itemize}

	% question 51
	\item An Amazon EC2 instance running the Amazon Linux 2 AMI is billed in what increment?

	\begin{itemize}
	\item Per second
\end{itemize}

	% question 52
	\item Which type of storage stores objects comprised of key, value pairs?

	\begin{itemize}
	\item Amazon S3
\end{itemize}

	% question 53
	\item Which Amazon EC2 Reserved Instance type enables you to match your capacity reservation to predictable recurring dates and times?

	\begin{itemize}
	\item Scheduled RI
\end{itemize}

	% question 54
	\item Which statement is correct in relation to the AWS Shared Responsibility Model?

	\begin{itemize}
	\item AWS are responsible for the security of regions and availability zones
\end{itemize}

	% question 55
	\item Which type of data storage system is typically considered to hold "structured" data?

	\begin{itemize}
	\item Relational database
\end{itemize}

	% question 56
	\item What is an example of scaling vertically?

	\begin{itemize}
	\item Increasing the instance size with Amazon RDS
\end{itemize}

	% question 57
	\item Which Amazon namespace is used to uniquely identify AWS resources?

	\begin{itemize}
	\item ARN
\end{itemize}

	% question 58
	\item Which of the below is Amazon's proprietary RDS database?

	\begin{itemize}
	\item Aurora
\end{itemize}

	% question 59
	\item 

	\begin{itemize}
	\item Amazon S3
	\item Amazon EC2
\end{itemize}

	% question 60
	\item Which resource should you use to access AWS security and compliance reports?

	\begin{itemize}
	\item AWS Artifact
\end{itemize}

	% question 61
	\item Which services are integrated with KMS encryption? (Select TWO.)

	\begin{itemize}
	\item Amazon RDS
	\item Amazon EBS
\end{itemize}

	% question 62
	\item Which of the options below are recommendations in the reliability pillar of the well-architected framework? (Select TWO.)

	\begin{itemize}
	\item Automatically recover from failure
	\item Manage change in automation
\end{itemize}

	% question 63
	\item Which service can be used to manage configuration versions?

	\begin{itemize}
	\item AWS Config
\end{itemize}

	% question 64
	\item Which service can be used to improve performance for users around the world?

	\begin{itemize}
	\item Amazon CloudFront
\end{itemize}

	% question 65
	\item Which of the following is an advantage of cloud computing compared to deploying your own infrastructure on-premise?

	\begin{itemize}
	\item Paying only for what you use
\end{itemize}

\end{enumerate}
